Integer-N PFD/CP-based PLL - System-Level simulation

### 2025-05-05 Examples/Example3_5_SystemPhaseNoiseCalculation/Report/article/article.qmd
Studying.

>>>>

So the maximum frequency step at the input such that the theory so far is still able to predict the behavior of the system is `{python} format(step_m_lin)`Hz. If the frequency step is any larger than this, then the PLL will lose lock and cycle slip, which is the

At other side, the settling time, $t_s$, can be calculated as

$$
t_s\approx\frac{-\ln\left(0.01\sqrt{1-\zeta^2}\right)}{\zeta}\frac{1}{\omega_n}
$$

t_s=math.log(0.01*math.sqrt(1-zeta**2), math.e)/(zeta*omega_n)*(-1)
```

resulting in a settling time of $t_s=$`{python} format(t_s)`s.

<!-- TODO: Prepare simulations to verify these responses -->
